Hochschild cohomology of torus equivariant D-modules: New approach

### 2017-10-06 rewrite.tex
Add stuff form old version and some new things.

\newcommand\cs{\stack{B}}
\newcommand\catCoSimplicial{\cat{\Delta}^{\mathrm{op}}}
\newcommand\dR{\mathrm{dR}}
\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
\newcommand{\HCoh}{\operatorname{HH}^\cx}   % Hochschild cohomology
\newcommand\opalg[1]{#1^{\mathrm{op}}}

@@

>>>>

\newcommand\cs{\stack{B}}
\newcommand\catCoSimplicial{\cat{\Delta}^{\mathrm{op}}}
\newcommand\dR{\mathrm{dR}}
\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
\newcommand{\HCoh}{\operatorname{HH}^\cx}   % Hochschild cohomology
\newcommand\opalg[1]{#1^{\mathrm{op}}}
\newcommand\LocSys{\operatorname{LocSys}}   % local systems
\newcommand\Bun{\operatorname{Bun}}         % bundles
\newcommand\dualize{\mathbb D}
\newcommand\Gammasub[1]{\Gamma_{\mkern-3mu#1}}
\newcommand\barGammasub[1]{\bar{\Gamma}_{\mkern-3mu#1}}

\renewcommand\ls[1]{\mathbfcal{L} #1}
\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
\newcommand\lsc[1]{\mathbfcal{L}^c #1}
\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}

\newcommand\goodness{property \textbf{(!)}}
\newcommand\goodnessshort{\textbf{(!)}}
\newcommand\isgood{has property \textbf{(!)}}
\newcommand\aregood{have property \textbf{(!)}}
\newcommand\isnotgood{does not have property \textbf{(!)}}
\newcommand\arenotgood{do not have property \textbf{(!)}}
\newcommand\goodX[1]{#1 with property \textbf{(!)}}
\newcommand\goodnessb{property \textbf{(!')}}
\newcommand\goodnessbshort{\textbf{(!')}}
\newcommand\isgoodb{has property \textbf{(!')}}
\newcommand\aregoodb{have property \textbf{(!')}}
\newcommand\goodbX[1]{#1 with property \textbf{(!')}}

\newcommand\XXtimes{%
    \mathchoice%
        {\mathop{×}\limits_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
        {×_{\stack X × \stack X}}
    }

% overrides
\let\shortbar\bar
\let\bar\overline

% Formatting of upper case roman numerals (in references).
\newcommand{\RomanNum}[1]{\textsc{\MakeLowercase{#1}}}

@@

\begin{abstract}
    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
    This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
\end{abstract}

\setcounter{tocdepth}{1}
\tableofcontents

\section{Introduction}

Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether the sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
For example, for constructible sheaves this leads to the notion of microsupport discussed in detail in \cite{KashiwaraSchapira:1994:SheavesOnManifolds}.
More generally, given a category of sheaves on a space $X$, we can ask whether it is possible to localize them on some space that is strictly larger than $X$ itself.

Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
For co-complete compactly generated triangulated categories one answer is provided by \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves).

We are led to consider the universal algebra acting on $\cat C$ by this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
\[
    \HCoh(\cat C)
    = \mathbb{R}\mathrm{Hom}(\id[\cat C], \id[\cat C])
    = \Hom_{\cat{Funct}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
\]
The ring $R = \bigoplus \operatorname{HH}^{2n}(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
Thus understanding the Hochschild cohomology of a dg category can be an important step to understanding the category itself.

This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.

A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
Representing the identity functor by its kernel, we obtain an isomorphism of dg algebras
\begin{equation}
    \label{eq:intro:d-mod-hcoh}
    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
\end{equation}
where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.

By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod-hcoh} as
\[
    \HCoh(\catDMod{\stack X}) \cong
    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
    \opalg{\GammadR(\stack X, Δ^!Δ_!k_{\stack X})}.
\]
It is now tempting to look at the Cartesian square
\[
    \begin{tikzcd}
        \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
where
\[
    \ls \stack X = \stack X \mathop{×}\limits_{\stack X × \stack X} \stack X
\]
is the derived loop space (or inertia stack) of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
We could expect the existence of an isomorphism
\begin{equation}
    \label{eq:intro:naive}
    \GammadR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
    \GammadR(\stack X, p_{1,!}p₂^! k_{\stack X}).
\end{equation}
We refer to this as the \enquote{naive expectation}.
Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\Ga$ is an easy counter-example).

In this paper we investigate how to quantify the cone of the morphism
\begin{equation}\label{eq:intro:central_cone}
    p_{1,!}p₂^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
\end{equation}
and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.

\begin{Thm}\label{thm:main}
    Let $G \cong \Gm^n$ be a torus acting on a normal scheme $X$ of finite type over $k$.
    Then there is a canonical isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{X/G}\bigr)
        \cong
        \opalg{\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)},
    \]
    where the algebra structure on $\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
\end{Thm}

Since, to the author's knowledge, there is currently no comprehensive account of the theory of D-modules on stacks available in the literature, we review the basic formalism in Section~\ref{sec:d-mods}.
In essence, most of the familiar six functor formalism of holonomic D-modules works in a general context.
It is convenient to rephrase Theorem~\ref{thm:main} as an equivalence of monads.
Thus in Section~\ref{sec:monads} we review some constructions of monads in our setting.
In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.

In Section~\ref{sec:base-change} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
Finally, in Section~\ref{sec:torus} we deduce Theorem~\ref{thm:main} from this description, using geometric considerations and the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.

The present paper represents only the first step in the study of Hochschild cohomology and associated support theories for D-modules.
In future work we intend to expand upon the foundations laid out in this paper.
Of particular interest are quotients stacks $X/G$ with $G$ an affine algebraic group and the stack $\Bun_G(C)$ of $G$-bundles on a curve $C$.
Following the constructions laid out in Section~\ref{sec:base-change:compactification}, for the former we need a good $G×G$-equivariant compactification of $G$.
Thus groups with a wonderful compactification are of particular interest for study with our methods.
For the latter, relative compactifications of the diagonal of $\Bun_G(C)$ have been proposed by Lafforgue and Drinfeld.
These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.% \cite{Gaitsgory:preprint:StrangeFunctionalEquationForEisensteinSeries}

\subsection*{Acknowledgments}
I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.

\section{D-modules on stacks}
\label{sec:d-mods}

We fix an algebraically closed base field $k$ of characteristic $0$.
All stacks will be assumed to be algebraic over $k$ and quasi-compact with affine automorphism group (QCA).
Thus by definition for any stack $\stack X$ we have:
\begin{itemize}
    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
    \item $\stack X$ is quasi-compact.
    \item The automorphism groups of the geometric points of $\stack X$ are affine.
    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
\end{itemize}
The QCA condition guarantees a reasonable theory of D-modules on $\stack X$.
For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.

In order to correctly define categories of D-modules on stacks it is necessary to work with dg-categories.
We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction.% \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}. %\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2014-draft:HigherAlgebra} to dg categories.
Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this article.

The category of D-modules on a stack $\stack X$ can be either constructed via descent \cite{BeilinsonDrifeld:unpublished:Hitchin,DrinfeldGaitsgory:2013:FinitenessQuestions} or equivalently as ind-coherent sheaves on the de Rham space of $\stack X$ \cite{GaitsgoryRozenblyum:2014:CrystalsAndDModules}.
While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.

For any morphism $f\colon \stack X → \stack Y$ we obtain a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
If $p\colon \stack X → \pt$ is the structure map, we set
\[
    \GammadR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
\]
The functor $\GammadR$ is representable by a D-module $k_{\stack X}$, i.e.
\[
    \GammadR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
\]
As $\GammadR(\stack X,\, {-})$ is usually not continuous and the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.

Let $Δ\colon \stack X → \stack X × \stack X$ be the diagonal.
The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product $\sheaf F \otimes \sheaf G \coloneq Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr)$ with unit $ω_{\stack X} = p^! k$.

We will be mainly concerned with the subcategory of holonomic D-modules since they enjoy extended functoriality.
\begin{Def}
    A $D$-module $\sheaf F ∈ \catDMod{\stack X}$ is called \emph{holonomic} if $f^!\sheaf F$ is holonomic for any smooth morphism $f\colon Z → \stack X$ from a scheme $Z$.
    The full subcategory of holonomic D-modules will be denoted $\catDModHol{\stack X}$.
\end{Def}

The following assertions mostly follow from their corresponding counterparts for schemes.
We refer to \cite{Braverman:LecturesOnAlgebraicDmodules} for proofs in the case of non-smooth schemes.

\begin{Prop}
    Let $f\colon \stack X → \stack Y$ be a schematic morphism.
    Then $f^!$ and $f_*$ restrict to functors
    \[
        f^!\colon \catDModHol{\stack Y} → \catDModHol{\stack X}
        \quad\text{and}\quad
        f_*\colon \catDModHol{\stack X} → \catDModHol{\stack Y}.
    \]
\end{Prop}

The Verdier duality functor on schemes induces an involutive anti-auto-equivalence
\[
    \dualize_{\stack X}\colon \catDModHol{\stack X}^\mathrm{op} → \catDModHol{\stack X}
\]
such that for each smooth morphism $Z → \stack X$ of relative dimension $d$ from a scheme $Z$ one has
\[
    f^! ∘ \dualize_{\stack X} \cong \dualize_{Z} ∘ f^![-2d].
\]
The Verdier duality functor then allows us to define the \emph{non-standard functors} $f_!$ and $f^*$ for any schematic morphism $f\colon \stack X → \stack Y$ by
\begin{align*}
    f^* & = \dualize_{\stack X} ∘ f^! ∘ \dualize_{\stack Y} \colon \catDModHol{\stack Y} → \catDModHol{\stack X} \\
    \intertext{and}
    f_! & = \dualize_{\stack Y} ∘ f_* ∘ \dualize_{\stack X} \colon \catDModHol{\stack X} → \catDModHol{\stack Y}.
\end{align*}
We obtain adjoint pairs $(f_!,\, f^!)$ and $(f^*,\, f_*)$.
In some situations we can identify the non-standard functors with their standard counterparts.
If $f$ is smooth of relative dimension $d$ then $f^* = f^![-2d]$.
If $f$ is proper then $f_! = f_*$ and in particular $f_*$ is left adjoint to $f^!$.
The objects $ω_{\stack X}$ and $k_{\stack X}$ are always holonomic and
\[
    \dualize_{\stack X} ω_{\stack X} = k_{\stack X}.
\]
We have $k_{\stack X} = f^* k_{\stack Y}$ and if $\stack X$ is smooth, then $k_{\stack X} = ω_{\stack X}[-2\dim \stack X]$.

We will make use of the following lemma which follows from \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions}.

\begin{Lem}
    For a smooth and schematic morphism $f$ the functor $f^!$ is conservative.
\end{Lem}

\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
    \label{prop:pre:base-change}%
    Consider a Cartesian square
    \[
        \begin{tikzcd}
            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
            \stack X₂ \arrow[r, "g"] & \stack Y
        \end{tikzcd}
    \]
    with schematic morphism $f$ (and hence $p$).
    Then there is a base change isomorphism
    \[
        p_* q^! \isoto g^! f_*
    \]
    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
    \[
        p_* q^! →
        p_* q^! f^! f_* =
        p_* p^! g^! f_* →
        g^! f_*
    \]
    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
    Similarly, if $f$ is an open immersion, then the base change isomorphism coincides with the natural transformation resulting from the adjunctions $(f^!,f_*)$ and $(p^!, p_*)$.
\end{Prop}

\begin{Prop}
    \label{prop:pre:projection-formula}%
    If $f\colon \stack X → \stack Y$ is a schematic morphism then the projection formula holds, i.e.~there is a functorial isomorphism
    \[
        \sheaf F \otimes f_*(\sheaf G) \cong f_*\bigl( f^! \sheaf F \otimes \sheaf G)
    \]
    for $\sheaf F ∈ \catDMod{\stack Y}$ and $\sheaf G ∈ \catDMod{\stack X}$.
\end{Prop}

\begin{Rem}
    Propositions \ref{prop:pre:base-change} and \ref{prop:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
    Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
    We fill not use either notion here and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
\end{Rem}

For D-modules on stacks we have the usual recollement package.
Let $i\colon \stack Z \hookrightarrow \stack X$ be a closed embedding and $j\colon \stack U \hookrightarrow \stack X$ the complementary open.
We have adjoint pairs $(i_*,\, i^!)$ and $(j^!,\, j_*)$.

\begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
    \label{prop:recollement-std}%
    There is an exact triangle of functors
    \[
        i_*i^! → \id → j_*j^!
    \]
    on $\catDMod{\stack X}$, the adjunction morphisms
    \[
        \id → i^!i_*
        \quad\text{and}\quad
        j^!j_* → \id
    \]
    are isomorphisms, the functors $j^!i_*$ and $i^!j_*$ vanish and $i_*$ and $j_*$ are full embeddings.
\end{Prop}

On holonomic D-modules we have the additional adjoint pairs $(i^*,\, i_*)$ and $(j_!,\, j^*)$.
By applying duality to Proposition~\ref{prop:recollement-std} we obtain the distinguished triangle
\[
    j_! j^* → \id → i_*i^*
\]
and the identity $i^*j_! = 0$ on holonomic D-modules.
Further, the functor $j_!$ is a full embedding $\catDModHol{\stack U} \hookrightarrow \catDModHol{\stack X}$.

\section{Monads}
\label{sec:monads}

We will deduce Theorem~\ref{thm:main} from a isomorphism of monads on $\catDMod{\stack X}$.
In this section we give a short introduction to the theory of monads and the specific constructions that we will use.
However, in the interest of readability we will mainly do so informally, skipping over the intricacies of $∞$-categories.
The interested reader can find the correct $∞$-categorical formulations in the given references.

Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
\begin{equation}
    \label{eq:pre:monad-identities}
    \begin{tikzcd}
        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
    \quad\text{and}\quad
    \begin{tikzcd}
        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
\end{equation}
commute.
Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.

Let $X$ be an object of the category $\cat C$.
Then $T$ gives the dg vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
\[
    (f,g) \mapsto μ_X ∘ Tf ∘ g,
\]
\[
    \begin{tikzcd}
        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
    \end{tikzcd}
\]
The identities~\ref{eq:pre:monad-identities} ensure that the algebra is associative and unital.

The most common source of monads is from a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
One simply sets $T = G ∘ F$ and $η$ and $μ$ are given by the adjunction morphisms
\[
    \id[\cat C] → G ∘ F = T
    \qquad\text{and}\qquad
    T² = G ∘ (F ∘ G) ∘ F → G ∘ F = T.
\]
We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2014-draft:HigherAlgebra}.
For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
\[
    \Hom_{\cat C}(X, (GF)(X)) \cong
    \Hom_{\cat D}(FX, FX).
\]

Another common way to obtain monads in geometry is via a groupoid.
Recall that a groupoid $G_{\cx}$ in stacks consists of a stack $\stack G₀$ of \enquote{objects} and a stack $\stack G₁$ of \enquote{morphisms} together with
\begin{itemize}
    \item \emph{source} and \emph{target} maps $s,t\colon \stack G₁ \rightrightarrows \stack G₀$,
    \item a \emph{unit} $e\colon G₀ → G₁$,
    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ \mathop{×}\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
    \item an \emph{inverse} map $ι\colon \stack G₁ → \stack G₁$,
\end{itemize}
such that
\begin{itemize}
    \item $s ∘ e = t ∘ e = \id_{\stack G₀}$,
    \item $s ∘ m = s ∘ p₂$ and $t ∘ m = t ∘ p₁$ (where $p_i\colon \stack G₁ ×_{s,\stack G₀,t} \stack G₁ → \stack G₁$ are the projection maps).
    \item $m$ is associative,
    \item $ι$ interchanges $s$ and $t$ and is an inverse for $m$,
\end{itemize}
where all identities have to be understood in the correct $∞$-categorical way \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory}.

\begin{Ex}
    For our purpose the most important example is the following:
    Let $f\colon \stack X → \stack S$ be a morphism of stacks.
    We set $\stack G_0 = \stack X$ and $\stack G₁ = \stack X ×_\stack S \stack X$.
    The source and target maps are given by $p₁$ and $p₂$, the unit by the diagonal $Δ\colon \stack X → \stack X×_\stack S\stack X$, the inverse by interchanging the factors and multiplication is $p₁₃\colon \stack X ×_\stack S \stack X ×_\stack S \stack X → \stack X×_\stack S\stack X$.
\end{Ex}

Let us for the moment assume that $s$ (and hence $t$) is proper and schematic.
In this case the maps $e$ and $m$ are also proper, since $s ∘ e = \id_{\stack G₀}$ and $s ∘ m = s ∘ p₂$ are proper.
In particular the functors $e^!\colon \catDMod{\stack G₁} → \catDMod{\stack G₀}$ and $m^!\colon \catDMod{\stack G₁} → \catDMod{\stack G₁ ×_{\stack G₀} \stack G₁}$ have left adjoints given by $e_*$ and $m_*$ respectively.
This allows us to give the endofunctor $T = s_*t^!$ of $\catDMod{\stack G₀}$ the structure of a monad in the following way:

\begin{itemize}
    \item By $(e_*,e^!)$-adjunction we have a transformation
        \[
            \id = (s∘e)_*(t∘e)^! = s_*e_*e^!t^! → s_*t^! = T.
        \]
    \item Consider the following commutative diagram
        \[
            \begin{tikzcd}[column sep=small]
                {} & & \stack G₁ \arrow[dddll, bend right, "s"] \arrow[dddrr, bend left, "t"] & & \\
                & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow[u, "m"] \arrow[dl, "p₂"] \arrow[dr, "p₁"] & & \\
                & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & \\
                \stack G₀ & & \stack G₀ & & \stack G₀
            \end{tikzcd}
        \]
        with Cartesian middle square.
        Proper base change and $(m_*,m^!)$-adjunction gives a transformation
        \[
            T² =
            s_*t^!s_*t^! =
            (s∘p₂)_*(t∘p₁)^! =
            (s∘m)_*(t∘m)^! =
            s_*m_*m^!t^! →
            s_*t^! =
            T.
        \]
\end{itemize}

In the non-$∞$-categorical setting one could easily check by hand that this is indeed a monad.
To obtain the corresponding derived statement one applies an argument similar to \cite[Section~\RomanNum{II}.1.7.2]{GaitsgoryRozenblyum:prelim:StudyInDAG}.

Let now $f\colon \stack X → \stack Y$ be schematic and proper.
The Cartesian diagram
\[
    \begin{tikzcd}
        \stack X ×_{\stack Y} \stack X \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack X \arrow[d, "f"] \\
        \stack X \arrow[r, "f"] & \stack Y
    \end{tikzcd}
\]
induces a groupoid with $\stack{G}₀ = \stack X$ and $\stack{G}₁ = \stack X ×_{\stack Y} \stack X$.
The above constructions now give two monads on $\catDMod{\stack{X}}$: one by $(f_*,f^!)$ adjunction and one from the groupoid structure.
The base change isomorphism
\[
    p_{t,*} p_s^! → f^! f_*
\]
gives an identification of these monads and hence of the algebras that they induce, i.e.~for any $\sheaf F ∈ \catDMod{\stack X}$ we have
\[
    \Hom(\sheaf F,\, p_{t,*} p_s^!\sheaf F) \cong
    \Hom(\sheaf F,\, f^! f_* \sheaf F) \cong
    \Hom(f_*\sheaf F,\, f_* \sheaf F).
\]

We will need to apply this construction for non-proper $f$.
Unfortunately, in this case none of the adjunctions used to define the monads are available.
We rectify this by restricting to the full subcategory of of holonomic D-modules and using the $!$-pushforward functors instead of the $*$-pushforward ones.
Of course, by doing so we do not automatically have base change isomorphisms available anymore.
Thus we have to explicitly require the \emph{Beck--Chevalley condition}, saying that all necessary base changes hold.

The Beck--Chevalley condition us formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
Intuitively, this is the simplicial stack, usually also denoted $\stack{G}_\cx$, with
\[
    \stack G_i = \underbrace{\stack G₁ ×_{\stack G₀} \dotsb ×_{\stack G₀} \stack G₁}_{\text{$i$ factors}}.
\]
We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
The following lemma is now an immediate corollary of \cite[Lemma~\RomanNum{II}.1.7.1.4]{GaitsgoryRozenblyum:prelim:StudyInDAG} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.

\begin{Lem}
    \label{lem:pre:groupoid_monad_hol}%
    Let $f\colon \stack X → \stack Y$ be a schematic morphism of stacks and let $\stack G_\cx$ be the corresponding groupoid.
    For each map $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ consider the corresponding square
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[r, "p_s"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
        \end{tikzcd}
    \]
    where the vertical arrows are induced by $F$.
    Assume that for each such square the base change composition
    \[
        p_{F+1,!} p_s^! →
        p_{F+1,!} p_s^! p_F^! p_{F,!} =
        p_{F+1,!} p_{F+1}^! p_s^!  p_{F,!} →
        p_s^! p_{F,!}
    \]
    given by the adjunction morphisms is an isomorphism of functors from $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
    Further assume that the same is true along 
    \[
        \begin{tikzcd}
            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
            \stack G₀ \arrow[r, "f"] & \stack Y
        \end{tikzcd}
    \]
    Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
\end{Lem}

\section{Hochschild cohomology}
\label{sec:HH}

We recall that the Hochschild cohomology of a dg category $\cat C$ is the algebra of derived endomorphisms of the identity functor,
\[
    \HCoh(\cat C) = \mathbb{R}\mathrm{Hom}(\id[\cat C],\, \id[\cat C]).
\]
For the exact definition of the category $\mathbb{R}\mathrm{Hom} = \cat{Funct}(\cat C, \cat C)$ we refer to \cite{Keller:2006:OnDGCategories}.
Instead we will give a more concrete construction via kernels which can be applied to $\catDMod{\stack X}$.
For this let us restrict to the case of co-complete dg categories and let $\cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)$ be the full subcategory of $\cat{Funct}(\cat C, \cat C)$ spanned by the continuous functors.
Then, since $\id[\cat C]$ is evidently continuous, we have
\[
    \HCoh(\cat C) =
    \Hom_{\cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
\]
Let us further assume that $\cat C$ is dualizable with dual $\cat C^\dual$.
Thus there is a unit map
\[
    η\colon \catVect → \cat C^\dual \otimes \cat C
\]
and a counit map
\[
    ε\colon \cat C^\dual \otimes \cat C → \catVect
\]
satisfying the usual compatibilities (cf.~\cite[Section~2]{BenZviNadler:arXiv:NonlinearTraces}).
Let $u = η(k)$.
To each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\id[\cat C^\dual] \otimes F(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
\[
    \cat C
    \xrightarrow{\id[\cat C] \otimes Q}
    \cat C \otimes \cat C^\dual \otimes \cat C
    \xrightarrow{ε \otimes \id[\cat C]}
    \cat C.
\]
These assignments are mutually inverse and give an equivalence of dg categories
\[
    \cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)
    \cong
    \cat C^\dual \otimes \cat C.
\]
In particular, the kernel for the identity is $u$ and hence we have
\[
    \HCoh(\cat C) =
    \Hom_{\cat C^\dual \otimes \cat C}(u, u).
\]
Let us now consider the case of $\cat C = \catDMod{\stack X}$ for a stack $\stack X$.
Let $p\colon \stack X → \pt$ be the structure morphism and $Δ\colon \stack X → \stack X × \stack X$ the diagonal.
By \cite[Section~8.4]{DrinfeldGaitsgory:2013:FinitenessQuestions} the category $\catDMod{\stack X}$ is dualizable and there is a canonical identification
\[
    \catDMod{\stack X}^\dual \otimes \catDMod{\stack X} \cong \catDMod{\stack X × \stack X}
\]
such that the unit map is given by $Δ_*p^!$, i.e.~we have
\[
    u = Δ_*ω_{\stack X}.
\]
We summarize the above discussion in the following lemma.

\begin{Lem}\label{lem:pre:hcoh}
    Let $\stack X$ be a stack.
    Then the Hochschild cohomology of $\catDMod{\stack X}$ is given by the dg algebra
    \[
        \HCoh(\catDMod{\stack X}) =
        \Hom_{\catDMod{\stack X × \stack X}}(Δ_*ω_{\stack X},\, Δ_*ω_{\stack X}).
    \]
\end{Lem}
